Comparative Analysis of Approximation Algorithms for Solving TSP

### 2018-04-28 tex/paper.tex
TSP shouldn't be followed by problm

	The algorithm implementation for solving the TSP problem is as follows:
	\begin{enumerate}
		\item Select a random city as the current city
		\item For all cities
		\item Select the closest unvisited city to the current one
		\item Mark current city as visited
		\item Visit the new selected city
		\item If all cities are visited then terminate
		\item O.W. go back to step 3
	\end{enumerate}

@@

	Datasets for TSP problem contain a wide variety of formats. Cities across a country, VLSI nodes or traveling across the Mona Lisa drawing are examples of these formats. But they are all similar in the data structure which is a 2-D coordinate point system with euclidean distances as the distance between nodes.
	For our work we selected the Uruguay dataset from the national dataset collection\cite{UY734} to be used to assess the four algorithms in this survey in terms of runtime performance and how close are their solutions compared to the dataset known optimal solution. Uruguay dataset is characterized by: 
	\begin{itemize}
		\item 734 unique points (no duplicates)
		\item Optimal tour of length 79,114
	\end{itemize}
	A graphical representation of the coordinates of the dataset is shown in figure \ref{fig:uruguay}
	\begin{figure}[h!]
		\centering
		\includegraphics[scale=0.3]{./uypoints.jpg}
		\caption{XY coordinate representation of Uruguay dataset}
		\label{fig:uruguay}
	\end{figure}

@@

	The codes to solve the TSP problem\cite{Kirk14}\cite{mathwork}\cite{Jang02}\cite{Jevtic14}\cite{Ibrahim15} were executed on both Matlab and Octave, taking into consideration the resulting output path length and the execution time. All the test conducted were repeated ten times each in order to see how well the algorithms can improve in both criteria. The generated path efficiency is calculated as the percentage of the increase in the resulting path length over the optimal path.
	$\frac{\textit{Detected Path Length} - \textit{Optimal Path Length}}{Detected Path Length} * 100 $

@@

		Jinhui Y., Xiaohu S., Maurizio M., Yanchun L.,\emph{An ant colony optimization method for generalized TSP problem}. (2008).

>>>>

	The algorithm implementation for solving the TSP is as follows:
	\begin{enumerate}
		\item Select a random city as the current city
		\item For all cities
		\item Select the closest unvisited city to the current one
		\item Mark current city as visited
		\item Visit the new selected city
		\item If all cities are visited then terminate
		\item O.W. go back to step 3
	\end{enumerate}

@@

	Datasets for TSP contain a wide variety of formats. Cities across a country, VLSI nodes or traveling across the Mona Lisa drawing are examples of these formats. But they are all similar in the data structure which is a 2-D coordinate point system with euclidean distances as the distance between nodes.
	For our work we selected the Uruguay dataset from the national dataset collection\cite{UY734} to be used to assess the four algorithms in this survey in terms of runtime performance and how close are their solutions compared to the dataset known optimal solution. Uruguay dataset is characterized by: 
	\begin{itemize}
		\item 734 unique points (no duplicates)
		\item Optimal tour of length 79,114
	\end{itemize}
	A graphical representation of the coordinates of the dataset is shown in figure \ref{fig:uruguay}
	\begin{figure}[h!]
		\centering
		\includegraphics[scale=0.3]{./uypoints.jpg}
		\caption{XY coordinate representation of Uruguay dataset}
		\label{fig:uruguay}
	\end{figure}

@@

	The codes to solve the TSP\cite{Kirk14}\cite{mathwork}\cite{Jang02}\cite{Jevtic14}\cite{Ibrahim15} were executed on both Matlab and Octave, taking into consideration the resulting output path length and the execution time. All the test conducted were repeated ten times each in order to see how well the algorithms can improve in both criteria. The generated path efficiency is calculated as the percentage of the increase in the resulting path length over the optimal path.
	$\frac{\textit{Detected Path Length} - \textit{Optimal Path Length}}{Detected Path Length} * 100 $

@@

		Jinhui Y., Xiaohu S., Maurizio M., Yanchun L.,\emph{An ant colony optimization method for generalized TSP}. (2008).
